Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 paper2.tex
change parameter table captions
footnote for finite part

In this chapter we consider the emulation of one-loop 
$e^+e^-\rightarrow Z / \gamma^{*} \rightarrow q\bar q +n_{g} g$
matrix elements for $n_{g}$ up to and including 3, which corresponds
to events with up to 5 partons. We denote the number of final-state
partons as $n$. Instead of emulating the matrix element itself we build
a surrogate for the related so-called $k$-factor
%More specifically, we consider the emulation
%of the one-loop k-factor
\begin{equation}
    k_{n} = \dfrac{2 \Re \left\{ \mathcal{M}^{(n, 0)} \mathcal{M}^{(n, 1)\, *} \right\} }{ |\mathcal{M}^{(n, 0)}|^{2} } \equiv \dfrac{|\mathcal{M}^{(n, 1)}|^{2}}{|\mathcal{M}^{(n, 0)}|^{2}} \, ,
    \label{eq:k_factor}
\end{equation}
where $\mathcal{M}^{(n, \ell)}$ denotes the amplitude
for a process with $n$ final-state partons, at loop-order
$\ell$. We will refer to the interference term in the numerator
as the one-loop matrix element henceforth and introduce
this notation for brevity.
The sum/averaging over colour and helicity is implicit for
both the one-loop matrix element and the tree-level
matrix element. The numerator in Eq. (\ref{eq:k_factor}) is the
finite part of the interference between the tree-level and 
one-loop level matrix element, where the conventional dimensional
regularisation (CDR) scheme is used.

@@

Generated phase-space points are fed to {\MadGraph} \cite{Alwall:2014hca,Hirschi:2011pa}
to compute the tree-level and one-loop level matrix elements.
For each phase-space point, we use the corresponding
renormalisation scale sampled and evaluate the strong coupling
constant at this scale using the NNPDF-4.0 NNLO PDF set
\cite{NNPDF:2021njg} with the LHAPDF6 interface \cite{Buckley:2014ana}.
The full set of parameters used to evaluate the matrix elements are
quoted in Table~\ref{table:fame2_params}.
\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
        \toprule
        Parameters & \\
        \midrule
        Scales & \makecell[l]{$\mu_{R}$ sampled logarithmically in range [$\log(\sqrt{s_{\text{com}}}/4)$, $\log(4\sqrt{s_{\text{com}}})$]} \\
        \midrule
        Masses & \makecell[l]{$m_{b} = 4.7$ GeV \\ $m_{t} = 173$ GeV \\ $m_{\tau} = 1.777$ GeV \\ $m_{Z} = 91.188$ GeV \\ $m_{W} = 80.419$ GeV \\ $m_{H} = 125$ GeV} \\
        \midrule
        Couplings & \makecell[l]{$\alpha_{s} = \alpha_{s}(\mu_{R}^{2})$ \\ $\alpha_{e} = 1/132.507$ \\ $G_{F} = 1.166390 \times 10 ^{-5}$ GeV$^{-2}$} \\
        \midrule
        Decay widths & \makecell[l]{$\Gamma_{t} = 1.4915$ GeV \\ $\Gamma_{Z} = 2.441404$ GeV \\ $\Gamma_{W} = 2.0467$ GeV \\ $\Gamma_{H} = 6.382339 \times 10^{-3}$ GeV} \\
        \bottomrule
        \end{tabular}
    \caption{List of parameters for the matrix element generation. Masses and decay widths not listed explicitly have been set to zero.}
    \label{table:fame2_params}
\end{table}

>>>>

In this chapter we consider the emulation of one-loop 
$e^+e^-\rightarrow Z / \gamma^{*} \rightarrow q\bar q +n_{g} g$
matrix elements for $n_{g}$ up to and including 3, which corresponds
to events with up to 5 partons. We denote the number of final-state
partons as $n$. Instead of emulating the matrix element itself we build
a surrogate for the related so-called $k$-factor
%More specifically, we consider the emulation
%of the one-loop k-factor
\begin{equation}
    k_{n} = \dfrac{2 \Re \left\{ \mathcal{M}^{(n, 0)} \mathcal{M}^{(n, 1)\, *} \right\} }{ |\mathcal{M}^{(n, 0)}|^{2} } \equiv \dfrac{|\mathcal{M}^{(n, 1)}|^{2}}{|\mathcal{M}^{(n, 0)}|^{2}} \, ,
    \label{eq:k_factor}
\end{equation}
where $\mathcal{M}^{(n, \ell)}$ denotes the amplitude
for a process with $n$ final-state partons, at loop-order
$\ell$. We will refer to the interference term in the numerator
as the one-loop matrix element henceforth and introduce
this notation for brevity.
The sum/averaging over colour and helicity is implicit for
both the one-loop matrix element and the tree-level
matrix element. The numerator in Eq. (\ref{eq:k_factor}) is the
finite part\footnote{See Section 3.2 and Appendix A.1 in Ref.~\cite{Hirschi:2011pa} for explicit definitions.}
of the interference between the tree-level and 
one-loop level matrix element, where the conventional dimensional
regularisation (CDR) scheme is used.

@@

Generated phase-space points are fed to {\MadGraph} \cite{Alwall:2014hca,Hirschi:2011pa}
to compute the tree-level and one-loop level matrix elements.
For each phase-space point, we use the corresponding
renormalisation scale sampled and evaluate the strong coupling
constant at this scale using the NNPDF-4.0 NNLO PDF set
\cite{NNPDF:2021njg} with the LHAPDF6 interface \cite{Buckley:2014ana}.
The full set of parameters used to evaluate the matrix elements are
quoted in Table~\ref{table:fame2_params}.
\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
        \toprule
        Parameters & \\
        \midrule
        Scales & \makecell[l]{$\mu_{R}$ sampled logarithmically in range [$\log(\sqrt{s_{\text{com}}}/4)$, $\log(4\sqrt{s_{\text{com}}})$]} \\
        \midrule
        Masses & \makecell[l]{$m_{b} = 4.7$ GeV \\ $m_{t} = 173$ GeV \\ $m_{\tau} = 1.777$ GeV \\ $m_{Z} = 91.188$ GeV \\ $m_{W} = 80.419$ GeV \\ $m_{H} = 125$ GeV} \\
        \midrule
        Couplings & \makecell[l]{$\alpha_{s} = \alpha_{s}(\mu_{R}^{2})$ \\ $\alpha_{e} = 1/132.507$ \\ $G_{F} = 1.166390 \times 10 ^{-5}$ GeV$^{-2}$} \\
        \midrule
        Decay widths & \makecell[l]{$\Gamma_{t} = 1.4915$ GeV \\ $\Gamma_{Z} = 2.441404$ GeV \\ $\Gamma_{W} = 2.0467$ GeV \\ $\Gamma_{H} = 6.382339 \times 10^{-3}$ GeV} \\
        \bottomrule
        \end{tabular}
    \caption{List of parameters used for matrix element generation for all processes. $\alpha_{s}$ is evaluated with the NNPDF-4.0 NNLO PDF set. Masses and decay widths not listed explicitly have been set to zero.}
    \label{table:fame2_params}
\end{table}
